### 2016-08-29 version0.0/paper1.tex
Applying P.W's Comments on chapter2

\citet{Draine14} produced two dust maps of M31 using MIPS-160 resolution (FWHM  39\arcsec; 18\arcsec $\times$ 18\arcsec pixels) and SPIRE 350 resolution (FWHM 24\arcsec.9; 10\arcsec $\times$ 10\arcsec pixels), which are publicly available. 
We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\textsc i} map, then divided this dust mass by the mass of hydrogen in M31. 
However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citet{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2. We divided our dust map by 2 to account for this correction. 
We then generated a metallicity map of M31 by using the dust map in combination with equation~\ref{equ: metal}. \citet{Draine14} showed that with increasing distance from the centre of M31, the dust to H mass ratio declines monotonically and concluded that metallicity also behaves in the same way. 
Their fitting results showed that M31 can be divided into three regions ($R< 8~\kpc$, $8~\kpc < R < 18~\kpc$, and $18~\kpc < R < 25~\kpc$) where the dust to H mass ratio (or metallicity) has a different correlation with galactocentric distance.

@@

As mentioned before, the K-S law in M31 has been tested by many groups. In one of the most recent works on M31, \citet{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares fitting method. 
To make a meaningful comparison between our results and the results reported in \citet{Ford13}, we averaged the power-law indices in \citet{Ford13} with a certain annuli and compared to the results with the same annuli in ours. We calculated power-law indices to be in the case of the H$_{2}$-only gas $N \sim 0.35, 0.58, 0.68$ and in case of total gas, $N \sim 1.37, 2.05, 1.60$ for $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$, respectively.
\citet{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have some differences with results from \citet{Ford13}. \citet{Ford13} argued that the main reason for these differences is the cut-off they used to fit the data.

>>>>

\citet{Draine14} produced two dust maps of M31 using MIPS-160 resolution (FWHM  39\arcsec; 18\arcsec $\times$ 18\arcsec pixels) and SPIRE 350 resolution (FWHM 24\arcsec.9; 10\arcsec $\times$ 10\arcsec pixels), which are publicly available. 
We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\textsc i} map, then divided this dust mass by the mass of hydrogen in M31. 
However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citep{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2. We divided our dust map by 2 to account for this correction. 
We then generated a metallicity map of M31 by using the dust map in combination with equation~\ref{equ: metal}. \citet{Draine14} showed that with increasing distance from the centre of M31, the dust to H mass ratio declines monotonically and concluded that metallicity also behaves in the same way. 
Their fitting results showed that M31 can be divided into three regions ($R< 8~\kpc$, $8~\kpc < R < 18~\kpc$, and $18~\kpc < R < 25~\kpc$) where the dust to H mass ratio (or metallicity) has a different correlation with galactocentric distance.

@@

As mentioned before, the K-S law in M31 has been tested by many groups. In one of the most recent works on M31, \citet{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares fitting method. 
To make a meaningful comparison between our results and the results reported in \citet{Ford13}, we averaged the power-law indices in \citet{Ford13} by a certain annuli and compared to the results with the same annuli in ours. We calculated power-law indices to be in the case of the H$_{2}$-only gas $N \sim 0.35, 0.58, 0.68$ and in case of total gas, $N \sim 1.37, 2.05, 1.60$ for $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$, respectively.
\citet{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have some differences with results from \citet{Ford13}. \citet{Ford13} argued that the main reason for these differences is the cut-off they used to fit the data.
